Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-02 p2/axioms.tex
New script to enumerate references
Rename "works" to "defined"

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mylem}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
% TODO APPENDIX
If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we know $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
\end{proof}

>>>>

So that we can describe the effects of commands independently of filesystems,
let us introduce some notation
and note some observations.
We already know that
commands usually do not occur in isolation,
and are applied to filesystems in time.
Therefore we investigate sequences of commands with a well-defined order.
\begin{mydef}[Sequences of commands: $\cc$ and $\emptyseq$]
We use ``$\cc$'' to combine commands to form a sequence, or combine sequences to form a longer sequence,
with the meaning that the command on the left is applied first:
\[ \alpha\cc\beta\aFS = \beta(\alpha\aFS). \]
% For example, we will write
% $S=\cbdaa{n}\cc\cbfaa{m}$, or $S'=S\cc\cbba{o}$.
%% monoid, but not free monoid
%% monoid: semigroup with identity element
%% Sequences of commands form a free semigroup
Sequences are also partial endofunctions on filesystems, defined only if all commands succeed.
We write $\sets$ for the set of sequences of commands.
They form a monoid, and, as usual,
$\emptyseq$ denotes its unit element, the empty sequence,
which is defined on all filesystems and by definition leaves all filesystems unchanged.
\end{mydef}

@@

\begin{mylem}\label{equiv_on_fs}
$A\equiv B$
iff $A$ and $B$ behave in the same way on
all filesystems, that is, $\forall \FS: A\aFS=B\aFS$.
\end{mylem}
\begin{proof}
% TODO APPENDIX
If $\forall \FS: A\aFS=B\aFS$, then $A\eqext B$ and $B\eqext A$ and so by definition $A\equiv B$.
For the reverse statement we know $A\eqext B$ and $B\eqext A$.
$B\eqext A$ implies that it is not possible for both $B\aFS\neq\fsbroken$ and $A\aFS=\fsbroken$ to be true.
Therefore, for every filesystem $\FS$, either $A\aFS\neq\fsbroken$, in which case $A\aFS=B\aFS$ as $A\eqext B$, or $A\aFS=\fsbroken$,
in which case $B\aFS=\fsbroken$ must be true, and therefore $A\aFS=B\aFS$.
\end{proof}

### 2017-10-02 p2/rec-complete.tex
Minor updates
New definitions based on equivalence classes
Rename "works" to "defined"

The reconciliation algorithm defined above is also maximal, that is,
it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
To show this, we are going to prove the following \namecref{rec_is_complete}:

@@

First, we prove that this sequence breaks all filesystems
unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence works on $\FS$ where $A\aFS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also work.

We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
As the sequence works, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
As $\czwmv$ and $T_0$ originate from $\bmanp$ and $B$ is simple, we also know there are
no commands on $m$ in $\acbnp$ or $T_0$,
and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.

On the one hand we therefore know that $\FS(m)$ must be of type $Z$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

Clearly $Q=Z$ (from \cref{worksinputmatch}), and from the construction and destruction
pairs we also see that $R=W$ must hold, where $W=\cchard$ or $W=\ccharb$.
As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
$\cqrmv = \czwmv$.
This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.

The only possibility is therefore $n=m$.
As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
and so (again from \cref{worksinputmatch}) $Z=X$.
We also know $\valvw\neq\valvy$ as otherwise the two commands would be equal and
would be included in $\acbnp$,
but this means that $\cxynv$, from $A$, overrides a change introduced 
by $\czwnv$, from $B$, which should be treated as a conflict.
\end{proof}

>>>>

%% TODO general properties of commands ==> behavior on specific filesystems

The reconciliation algorithm defined above is also maximal, that is,
it is not possible to apply any further commands from $A\setminus B$ to $\FS_B$.
To show this, we are going to prove the following theorem:

@@

First, we prove that this sequence breaks all filesystems
unless $n=m$.
Let us therefore suppose $n\neq m$ and, to use an inverse proof,
that the sequence is defined on $\FS$ where $A\aFS\neq\fsbroken$.
If so, its initial segment, $\acb\cc S_0\cc T_0 \cc \czwmv \cc \cxynv$ must also be defined.

We know $\cxynv\nindep\czwmv$, and so from \cref{incomparable_is_independent}, $n\nunrel m$.
As the sequence is defined, $\czwmv\cc\cxynv$ can only be a construction or destruction pair.
As $\czwmv$ and $T_0$ originate from $\bmanp$ and $B$ is simple, we also know there are
no commands on $m$ in $\acbnp$ or $T_0$,
and that there are no commands on $m$ in $S_0$ as $S_0\indep\bma$.

On the one hand we therefore know that $\FS(m)$ must be of type $[z]$,
but on the other, from \cref{ax_directchild_breaks,ax_directparent_breaks},
we also know that $\cxynv$ cannot be applied to $\FS$ without
changing $\FS(m)$ first.
As $A\aFS\neq\fsbroken$, this means that $A$ must contain a command on $m$.
Let this command be $\cqrmv$.

Clearly $[q]=[z]$ (from \cref{worksinputmatch}), and from the construction and destruction
pairs we also see that $r=w$ must hold, where $w=\vald$ or $w=\empt$.
As $|\setd|=1$ and $|\setb|=1$, this also means that $v_R=v_W$ and therefore
$\cqrmv = \czwmv$.
This is a contradiction as $\cqrmv\in A$, but $\czwmv\in\bmanp$.

The only possibility is therefore $n=m$.
As $A$ and $B$ are simple, we therefore know that these are the first commands on $n$,
and so (again from \cref{worksinputmatch}) $[z]=[x]$.
We also know $w\neq y$ as otherwise the two commands would be equal and
would be included in $\acbnp$,
but this means that $\cxynv$, from $A$, overrides a change introduced 
by $\czwnv$, from $B$, which should be treated as a conflict.
\end{proof}

### 2017-10-02 p2/rec-intro.tex
Improved notation
Rename "works" to "defined"

We assume that $A$ and $B$ are returned by an update detector,
and so they are simple sequences.
(Otherwise, they can be simplified to become simple sequences; see \cref{update_works}.)
We also assume that $\FS_A$ and $\FS_B$ are not broken.
With these assumptions,
we can now define our reconciliation algorithm.

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\begin{align*}
\reca = \{\alpha|{}& \\
& \alpha\in A\setminus B \\
& \wedge \\
& \forall \beta\in B\setminus A: \alpha\indep\beta\\
\}. &
\end{align*}
\end{mydef}

Whether two commands are independent is easy to determine programmatically
either based on \cref{def_indep} and the rules listed in \cref{section_axioms},
or based on \cref{incomparable_is_independent} 
in at most $O(x^2)$ time, where $x$ is the number of commands.
Then, to generate the sequence $\reca$ from the resulting set, 
we can order the commands using the algorithm described in
\cref{ordering} as any subset of $A$ is also simple.

>>>>

We assume that $A$ and $B$ are returned by an update detector,
and so they are simple sequences.
% TODO
(Otherwise, they can be simplified to become simple sequences; see \cref{update_works}.)
We also assume that $\FS$, $\FS_A$ and $\FS_B$ are not broken.
With these assumptions,
we can now define our reconciliation algorithm.

\begin{mydef}[Reconciliation]\label{def:reconciliation}
We determine $\reca$---which we apply to $\FS_B$ 
to reconcile it with $\FS_A$---to be
the largest subset of $A\setminus B$
that is independent of $B\setminus A$,
where $A$ and $B$ are simple sequences representing
the updates applied to replicas $\FS_A$ and $\FS_B$:
\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
\end{mydef}

Whether two commands are independent is easy to determine programmatically
either based on \cref{def_indep} and the rules listed in \cref{section_axioms},
or based on \cref{incomparable_is_independent} 
in at most $O(x^2)$ time, where $x$ is the number of commands.
Then, to generate the sequence $\reca$ from the resulting set, 
we can order the commands using the algorithm described in
\cref{ordering} as $\reca$, being a subset of $A$, is also simple.

### 2017-10-02 p2/rec-sound.tex
New script to enumerate references
Rename "works" to "defined"

We are now ready to prove that the proposed algorithm for reconciliation is correct,
that is, applying its result is not going to break the replicas.
We reformulate the original proposition, $\reca\aFS_B\neq\fsbroken$,
based on $\FS_B=B\aFS$ and so we aim to prove that
$B\cc\reca$ works wherever $A$ and $B$ work:

\begin{myth}
If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
\end{myth}

@@

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
Then their intersection, in some suitable order, also works on any filesystem
either of them works on:
$\worksm{A}{\acbnp}$, and, by symmetry,
$\worksm{B}{\acbnp}$.
\end{mylem}

@@

In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
If $B$ has a command on $m$, then
-- TODO TODO TODO --
from \cref{lemma:neighbor}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
When describing our ordering algorithm in \cref{ordering} we saw
that the command on the parent path determines whether a pair of commands
is a construction or destruction pair,
and that this, in turn, determines whether the command on the child path must
precede or follow the other command as otherwise the sequence would break all filesystems.
This argument holds for both $A$ and $B$, and so the command on $m$ must be on
the same side of the command on $n$ in both sequences.

@@

@@

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksmxb{\sqs{C}}{S^*}. \]
\end{mylem}

>>>>

We are now ready to prove that the proposed algorithm for reconciliation is correct,
that is, applying its result is not going to break the replicas.
We reformulate the original proposition, $\reca\aFS_B\neq\fsbroken$,
based on $\FS_B=B\aFS$ and so we aim to prove that
$B\cc\reca$ is defined wherever $A$ and $B$ are defined:

\begin{myth}\label{reconciliation_correct}
If $A, B$ are simple, then $\worksmbb{A,B}{B\cc \reca}$,
where, to restate \cref{def:reconciliation},
\[ \reca = \{\alpha \whr \alpha\in \ambnp  \ \wedge\   \alpha\indep \bmanp \}. \]
\end{myth}

@@

\begin{mylem}\label{can_move_intersection}
Let $A$ and $B$ be two simple sequences so that $\worksmnilb{A, B}$.
Then their intersection, in some suitable order, is also defined on any filesystem
either of them is defined on:
$\worksm{A}{\orderset{\acbnp}}$, and, by symmetry,
$\worksm{B}{\orderset{\acbnp}}$.
\end{mylem}

@@

In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
If $B$ has a command on $m$, then
-- TODO TODO TODO --
from \cref{lemma:neighbor}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
-- TODO TODO TODO --
When describing our ordering algorithm in \cref{ordering} we saw
that the command on the parent path determines whether a pair of commands
is a construction or destruction pair,
and that this, in turn, determines whether the command on the child path must
precede or follow the other command as otherwise the sequence would break all filesystems.
This argument holds for both $A$ and $B$, and so the command on $m$ must be on
the same side of the command on $n$ in both sequences.

@@

% TODO Set or sequence? See also above

@@

Our theorem is therefore proven if we prove the following lemma,
in which we rename $\ambnp$ to $S$ and $\bmanp$ to $T$:
\newcommand{\condSimple}{(c1)}
\newcommand{\condDisj}{(c2)}
\newcommand{\condApr}{(c3)}
\newcommand{\condWork}{(c4)}
\begin{mylem}\label{reconciliation_correct_part}
If
   \begin{itemize}
   \item[\condSimple] $S$ and $T$ are simple sequences,
   \item[\condDisj] $S\cap T=\emptyset$,
   \item[\condApr] $S^*$ is the largest subset of $S$ where $S^*\indep T$, and
   \item[\condWork] $\worksmxb{\sqs{C}}{S,T}$ for some set of sequences $\sqs{C}$,
   \end{itemize}
then
\[ \worksmxb{\sqs{C}}{S^*}. \]
\end{mylem}

### 2017-10-02 p2/works-inverse.tex
Rename "works" to "defined"

\begin{mydef}[$\worksmsign$, $\worksmeqsign$]\label{def_works}
For two sets of sequences $\sqs{A}$ and $\sqs{B}$
we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
that is, if all sequences in $\sqs{B}$ work (do not break the filesystem)
on any filesystem all sequences in $\sqs{A}$ work on.
We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.

As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is a filesystem
all sequences in $\sqs{A}$ work on.
We also apply these relations to sequences directly:
$\worksm{A}{B}$ with the meaning $\worksm{\{A\}}{\{B\}}$.
\end{mydef}

In a sense, $A\worksmeqsign B$ is a weaker counterpart of $A\eqext B$, as the former
only requires that $B$ works where $A$ works, where the latter also requires
that where they work, their effect is the same.
It is easy to see that the following corollary is true:

\begin{mycor}\label{worksextpostfix}
% An inference rule in the algebra
$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence works, its initial segment also works.
\end{mycor}

@@

\begin{myax}\label{combine_independent_commands}
The combination of independent commands works wherever both of the commands work:
\[ \alpha\indep \beta \Rightarrow \worksm{\{\alpha, \beta\}}{\{\alpha\cc \beta\}}. \]
\end{myax}
\begin{proof}
We name this proposition a \namecref{combine_independent_commands} 
because to prove it, we must reach back to our filesystem model.
Let $\alpha=\cxynv$ and $\beta=\czwmv$.
We prove the proposition by contradiction and
assume that there is a filesystem $\FS$ for which
$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
$\cxynv\cc \czwmv\aFS=\fsbroken$.
We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
$\czwmv$ that breaks it.
Applying a command can only result in a broken filesystem in two cases.
First, if the input type does not match the filesystem,
but we know $[\FS(m)]=[w]$ and so
$[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
Second, if the new filesystem violates the tree property.
This again cannot be the case because we also know that $n\unrel m$
and the tree property only depends on the types of values at the parent and children of $m$,
which therefore cannot be changed by $\cxynv$.
\end{proof}

@@

\begin{mylem}\label{combine_independent_sequences}
The combination of independent sequences works wherever both of the sequences work:
\[ S\indep T \Rightarrow \worksm{\{S,T\}}{\{S\cc T\}}. \]
\end{mylem}
\begin{proof}
Assume that there is a filesystem $\FS$ so that
$S\aFS\neq\fsbroken$ and $T\aFS\neq\fsbroken$, but
$(S\cc T)\FS=\fsbroken$.

@@

Let the command that breaks $\FS$ in $T$ when applying $S\cc T$ be $t$
so that $T=T_0\cc t\cc T_1$.
It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
and by definition $(S\cc T_0)\FS\neq\fsbroken$,
but $(S\cc T_0\cc t)\FS=\fsbroken$.
Also, from above we know that $S\cc T_0\equiv T_0\cc S$
and so $(T_0 \cc S)\FS\neq\fsbroken$.

@@

It is easy to see that for all objects where it is defined, $a\T\typeeq a$.
% $|\setf|$ is also $1$.
As representatives of filesystems, commands, sequences, etc.
are subsets of their non-representative counterparts, all
propositions proven so far apply to them as well.

@@

% TODO \alpha \neq \cbrk
\begin{mylem}\label{repr_comm_inject}
Representative commands $\alpha\T$ are partial bijections over representative filesystems ($\FS\T$).
Because partial functions are trivially surjective when restricted to their images, this is
equivalent to saying that representative functions are injective except for cases
where they break a filesystem (they are not defined):
\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
\end{mylem}
\begin{proof}
Let $\alpha\T = \cTxynv$.
If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
even after applying $\cTxynv$ to $\FS\T$. The only remaining case therefore is where they have the same values
at all nodes except $n$.
As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore, as there is a one-to-one correspondence between values and types,
$[\GS\T(n)]\neq[x]$.
This implies $\cTxynv(\GS\T)=\fsbroken$,
and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
\end{proof}

@@

Unless $\worksmnil{\ia}$, the propositions is trivially true. Otherwise,
for the left-to-right part of the proposition,
we know $\worksmnil{B\cc\ic}$, which implies that $\Dom{\ic}$ intersects with $\Img{B}$ 
as otherwise $B\cc\ic$ would break all filesystems.
As the (representative) $B$ is a bijection between its domain and image,
we can use $\ibi$ to map this intersection back
onto the domain of $B$ and get $\Dom{B\cc\ic}$.
As $\worksm{\ia}{B\cc\ic}$, 
we also know that $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
We now use $B$ to map both sides of this statement, which yields
$\Dom{B^{-1}\cc\ia} \subseteq \Dom{\ibi\cc B\cc\ic}$,
but the latter is a subset of $\Dom{\ic}$,
and so $\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$,
which is the same as $\worksm{\ibi\cc\ia}{\ic}$.

For the right-to-left part,
from $\worksm{\ia}{B}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
Therefore we can project the whole of $\Dom{\ia}$ using the bijective representative sequence $B$
to get $\Dom{\ibi\cc\ia}$, and as $\worksm{\ibi\cc\ia}{\ic}$
we know
$\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$.
We use $\ibi$ to project both sides of this statement to get
$\Dom{B\cc\ibi\cc\ia} \subseteq \Dom{B\cc\ic}$.
But we also know that $\Dom{B\cc\ibi\cc\ia} = \Dom{\ia}$
as $\Dom{\ia} \subseteq \Dom{B}$,
and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which is the same as
$\worksm{\ia}{B\cc\ic}$.
\end{proof}

@@

\begin{mylem}\label{indep_prefix_combine}
The combination of sequences with a common head and independent tails 
continues to work under the same conditions:
\begin{gather*}
 \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
 \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
\end{gather*}
\end{mylem}
\begin{proof}
Based on \cref{repr_works_is_same} we have
$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
and from \cref{r_invmove} we know
$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
Using \cref{combine_independent_sequences} we get
$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
and chaining these (as $\worksmeqsign$ is transitive)
we get
$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.

>>>>

\begin{mydef}[$\worksmsign$, $\worksmeqsign$]\label{def_works}
For two sets of sequences $\sqs{A}$ and $\sqs{B}$
we write $\worksm{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subseteq \Dom{\sqs{B}}$;
that is, iff all sequences in $\sqs{B}$ are defined on (that is, do not break)
all filesystems sequences in $\sqs{A}$ are defined on.
We write $\worksmstr{\sqs{A}}{\sqs{B}}$ iff $\Dom{\sqs{A}} \subset \Dom{\sqs{B}}$.

As a special case, we write $\worksmnil{\sqs{A}}$ if we know that there is at least one filesystem
all sequences in $\sqs{A}$ are defined on.
We also apply these relations to sequences directly;
e.g. we write
$\worksm{A}{B}$ with the meaning $\worksm{\{A\}}{\{B\}}$.
\end{mydef}

In a sense, $A\worksmeqsign B$ is a weaker counterpart of $A\eqext B$, as the former
only requires that $B$ is defined where $A$ is defined, where the latter also requires
that where they are defined, their effect is the same.
It is easy to see that the following corollary is true:

\begin{mycor}\label{worksextpostfix}
% An inference rule in the algebra
$\forall A,S: \worksm{A\cc S}{A}$, that is, if a sequence is defined,
its initial segment is also defined.
\end{mycor}

@@

\begin{myax}\label{combine_independent_commands}
The combination of independent commands is defined on all filesystems
where both of the commands are defined:
\[ \alpha\indep \beta \Rightarrow \worksm{\{\alpha, \beta\}}{\{\alpha\cc \beta\}}. \]
\end{myax}
\begin{proof}
We name this proposition a \namecref{combine_independent_commands} 
because to prove it, we must reach back to our filesystem model.
Let $\alpha=\cxynv$ and $\beta=\czwmv$.
We prove the proposition by contradiction and
assume that there is a filesystem $\FS$ for which
$\cxynv\aFS\neq\fsbroken$ and $\czwmv\aFS\neq\fsbroken$, but
$\cxynv\cc \czwmv\aFS=\fsbroken$.
We know $\cxynv\aFS\neq\fsbroken$ so it must be applying 
$\czwmv$ that breaks it.
Applying a command can only result in a broken filesystem in two cases.
First, if the input type does not match the filesystem,
but we know $[\FS(m)]=[w]$ and so
$[(\cxynv\aFS)(m)]=[w]$ as based on \cref{incomparable_is_independent}, $n\neq m$.
Second, if the new filesystem violates the tree property.
This again cannot be the case because we also know that $n\unrel m$
and the tree property only depends on the types of values at the parent and children of $m$,
which therefore cannot be changed by $\cxynv$.
\end{proof}

@@

\begin{mylem}\label{combine_independent_sequences}
The combination of independent sequences is defined on all filesystems
where both of the sequences are defined:
\[ S\indep T \Rightarrow \worksm{\{S,T\}}{\{S\cc T\}}. \]
\end{mylem}
\begin{proof}
Assume that there is a filesystem $\FS$ so that
$S\aFS\neq\fsbroken$ and $T\aFS\neq\fsbroken$, but
$(S\cc T)\FS=\fsbroken$.

@@

Let the command in $T$ that breaks $\FS$ when applying $S\cc T$ be $t$
so that $T=T_0\cc t\cc T_1$.
It is still true that $(T_0 \cc t)\FS\neq\fsbroken$,
and by definition $(S\cc T_0)\FS\neq\fsbroken$,
but $(S\cc T_0\cc t)\FS=\fsbroken$.
Also, from above we know that $S\cc T_0\equiv T_0\cc S$
and so $(T_0 \cc S)\FS\neq\fsbroken$.

@@

By definiton, for all objects where it is defined, $a\T\typeeq a$.
% $|\setf|$ is also $1$.
As representatives of filesystems, commands, sequences, etc.
are subsets of their non-representative counterparts, all
propositions proven so far apply to them as well.

@@

% TODO \alpha \neq \cbrk
\begin{mylem}\label{repr_comm_inject}
Representative commands $\alpha\T$ are partial bijections over representative filesystems ($\FS\T$).
Because partial functions are trivially surjective when restricted to their images, this is
equivalent to saying that representative functions are injective except for cases
where they break a filesystem (they are not defined):
\[ \forall\FS,\GS,\alpha: \FS\T\neq\GS\T \wedge \alpha\T(\FS\T)\neq\fsbroken \Longrightarrow \alpha\T(\FS\T) \neq \alpha\T(\GS\T). \]
\end{mylem}
\begin{proof}
Choose values that satisfy the left side, and let $\alpha\T = \cTxynv$.
If $\FS\T$ and $\GS\T$ have different values at any node apart from $n$, then this difference remains
even after applying $\cTxynv$ to $\FS\T$. 
The only remaining case therefore is where they have the same values
at all nodes except at $n$.
As $\cTxynv(\FS\T)\neq\fsbroken$, we know $[\FS\T(n)]=[x]$.
We also know that $\GS\T(n)\neq\FS\T(n)$, and therefore, as there is a one-to-one correspondence between values and types,
$[\GS\T(n)]\neq[x]$.
This implies $\cTxynv(\GS\T)=\fsbroken$,
and again we have $\alpha\T(\FS\T) \neq \alpha\T(\GS\T)$.
\end{proof}

@@

For the left-to-right part of the proposition,
from $\worksm{\ia}{B\cc\ic}$ we know $\Dom{\ia} \subseteq \Dom{B\cc\ic}$.
As the (representative) $B$ is a bijection between its domain and image,
we can use $B$ to map both sides of this statement, which yields
$\Dom{B^{-1}\cc\ia} \subseteq \Dom{\ibi\cc B\cc\ic}$,
but the latter is a subset of $\Dom{\ic}$,
and so $\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$,
which means that $\worksm{\ibi\cc\ia}{\ic}$.
It is easy to see that $\worksm{\ia}{B\cc\ic} \Leftrightarrow \worksm{\ia}{\{B\}}$.

For the right-to-left part,
from $\worksm{\ia}{\{B\}}$ we know $\Dom{\ia} \subseteq \Dom{B}$.
Therefore we can project the whole of $\Dom{\ia}$ using the bijective representative sequence $B$
to get $\Dom{\ibi\cc\ia}$, and as $\worksm{\ibi\cc\ia}{\ic}$
we know
$\Dom{\ibi\cc\ia} \subseteq \Dom{\ic}$.
We use $\ibi$ to project both sides of this statement to get
$\Dom{B\cc\ibi\cc\ia} \subseteq \Dom{B\cc\ic}$.
But we also know that $\Dom{B\cc\ibi\cc\ia} = \Dom{\ia}$
as $\Dom{\ia} \subseteq \Dom{B}$,
and so $\Dom{\ia} \subseteq \Dom{B\cc\ic}$ which means
$\worksm{\ia}{B\cc\ic}$.
\end{proof}

@@

\begin{mylem}\label{indep_prefix_combine}
The combination of two sequences with a common head and independent tails 
is defined wherever the two sequences are defined:
\begin{gather*}
 \worksmxb{\sqs{S}}{A\cc B} \,\wedge\, \worksmxb{\sqs{S}}{A\cc C} \,\wedge\, B\indep C \\
 \Longrightarrow \worksmxb{\sqs{S}}{A\cc B\cc C}
\end{gather*}
\end{mylem}
\begin{proof}
Based on \cref{repr_works_is_same} we have
$\worksmxb{\sqs{S}\T}{A\T\cc B\T}$ and $\worksmxb{\sqs{S}\T}{A\T\cc C\T}$,
and from \cref{r_invmove} we know
$\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{B\T}$ 
and $\worksmxb{{A\T}^{-1}\cc \sqs{S\T}}{C\T}$.
Using \cref{combine_independent_sequences} we get
$\worksmbb{B\T,C\T}{B\T\cc C\T}$,
and chaining these (as $\worksmeqsign$ is transitive)
we get
$\worksmxb{{A\T}^{-1}\cc \sqs{S}\T}{B\T\cc C\T}$.
